A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-05-29 sections/algorithm.tex
typos

Please note that when a new binder is introduced in the right-hand side worklist $\Gm'$,
we implicitly pick a fresh one,
since the right-hand side can be seen as the premise of the reduction.

>>>>

Please note that when a new variable is introduced in the right-hand side worklist $\Gm'$,
we implicitly pick a fresh one,
since the right-hand side can be seen as the premise of the reduction.
